---
title: "Birds and Bears Analysis"
author: "John Helveston"
output:
  html_document:
    toc: yes
    toc_float: yes
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	fig.path = "figs/",
	fig.retina = 3,
	message = FALSE,
	warning = FALSE,
	comment = "#>"
)
library(tidyverse)
library(here)
library(knitr)
bears <- read_csv(here::here('data', 'bear_killings.csv'))
birds <- read_csv(here::here('data', 'wildlife_impacts.csv'))
```

# Questions about birds

### Which months have the highest and lowest number of bird impacts with aircraft?

```{r bird-month-count, echo=FALSE}
birds %>% 
  count(incident_month) %>% 
  arrange(desc(n))

# birds %>% 
#   group_by(incident_month) %>% 
#   summarise(count = n())
```

The month with the most incidents is **September** and the month with the least is **December**

### Does the annual number of bird impacts appear to be changing over time?

```{r}
birds %>% 
  count(incident_year) %>% 
  arrange(desc(n))
```

# Questions about bears

### Which months have the highest frequency of bear killings?

```{r}
bears %>% 
  count(month) %>% 
  arrange(desc(n)) %>% 
  knitr::kable()
```

### Who has been killed more often by bears: hunters or hikers?

```{r}
bears %>% 
  count(hunter, hiker)
```

### How do the the number of bear attacks on men vs women compare?

```{r}
bears %>% 
  count(gender)
```

